---
title: "Smart Analysis"
#author: "Daniel Chen"
#date: ""
output: 
  html_document: 
    number_sections: yes
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, message=FALSE, warning=FALSE}
library(here)
library(broom)
library(dplyr)
library(tidyr)
library(ggplot2)
library(data.table)
library(printr) # make tables print prettier

ggplot2::theme_set(theme_bw())
knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 8, fig.height = 5 # golden ratio
                      )

# control how numbers are printed
options(scipen = 7, # penalty for showing decimal values in scientific notation (999 to disable)
        digits = 4 # number of sig figs
)

source(here('./R/smart_analysis.R'))
smart_dat <- readRDS(here('./data/mitre/final/logistic_regressions/smart_data_coefs.RDS'))
basel_dat <- readRDS(here('./data/mitre/final/logistic_regressions/basel_data_coefs.RDS'))
```

# Logistic Regression

## Coefficients

### Coefficient Summary Statistics

```{r}
summary_coefs(smart_dat, col = 'estimate_scaled')
```

```{r}
summary_coefs(basel_dat, col = 'estimate_scaled')
```

### OR Summary Statistics

```{r}
summary_coefs(smart_dat, 'or_scaled')
```

```{r}
summary_coefs(basel_dat, 'or_scaled')
```

### Plots

Jittered scatter plot of the coefficients from simulation runs (only along y)

```{r}
xlim1 <- floor(min(smart_dat$estimate_scaled, basel_dat$estimate_scaled))
xlim2 <- ceiling(max(smart_dat$estimate_scaled, basel_dat$estimate_scaled))

plot_sim_dat_jitter(smart_dat, 'estimate_scaled', 'SMART SCATTER: Coefficients for the Sumulation Runs', xlim = c(xlim1, xlim2))
plot_sim_dat_jitter(basel_dat, 'estimate_scaled', 'BASELINE: Coefficients for the Sumulation Runs', xlim = c(xlim1, xlim2))
```

```{r}
plot_sim_dat_hist(smart_dat, 'estimate_scaled', 'SMART SCATTER: Distribution of simulated coefficients')
plot_sim_dat_hist(basel_dat, 'estimate_scaled', 'BASELINE: Distribution of simulated coefficients')
```

### Proportion > 0

```{r}
prop_0(smart_dat, 'estimate_scaled', '>0')
prop_0(smart_dat, 'estimate_scaled', '<0')
```


### Proportion < 0

```{r}
prop_0(basel_dat, 'estimate_scaled', '>0')
prop_0(basel_dat, 'estimate_scaled', '<0')
```

## Odds Ratios

```{r}
xlim2 <- ceiling(max(smart_dat$or_scaled, basel_dat$or_scaled))
```


```{r}
plot_sim_dat_jitter(smart_dat, 'or_scaled', 'SMART SCATTER: ORs for the simulation runs', xlim = c(0, xlim2), vline = 1)
```

```{r}
plot_sim_dat_jitter(basel_dat, 'or_scaled', 'BASELINE: ORs for the simulation runs', xlim = c(0, xlim2), vline = 1)
```

### Disribution of ORs

```{r}
plot_sim_dat_hist(smart_dat, 'or_scaled', 'SMART SCATTER: Distribution of ORs') +
  geom_vline(aes(xintercept = 1), color = 'red')

plot_sim_dat_hist(basel_dat, 'or_scaled', 'BASELINE: Distribution of ORs') +
  geom_vline(aes(xintercept = 1), color = 'red')
```